% 3 Doors Down

\newsong{Here Without You}
  \beginverse*
    {\nolyrics \[Am F G]}
  \endverse

  \beginverse
    A hundred \[Am]days have made me older
    Since the last\[G] time that I saw your pretty face \[Am F G]
    A thousand \[Am]lies have made me colder
    And I \[G]don't think I can look at this the same\[Am F G]
    \[Am] All the miles that sepa\[G]rate
    \[Am] Disappear now when I'm d\[F]reamin' of y\[G]our face
  \endverse

  \beginchorus
    \[C] I'm here without you baby\[G]
    But you're still on my lonely m\[Am]ind
    I think about you baby
    \[F]And I dream a\[G]bout you all the time
    \[C] I'm here without you baby
    \[G] But you're still with me in my d\[Am]reams
    And t\[F]onight, there's \[G]only you and me
  \endchorus

  \beginverse*
    {\nolyrics \[Am G Am F G]}
  \endverse

  \beginverse
    The \[Am]miles just keep rollin'
    As the \[G]people leave their way to say he\[Am]llo \[F G]
    I've heard this \[Am]life is overrated
    But I \[G]hope that it gets better as we \[Am]go \[F G]
  \endverse

  \textnote{Chorus}

  \beginverse*
    \[Am] Everything I know,\[C] and anywhere I go
    \[G] It gets hard but it won't \[F]take away my love
    \[Am] And when the last one falls,\[C] when it's all said and \[G]done
    It gets hard but it won't \[F]take away my \[F]love \[C G Am F G]
  \endverse
  \textnote{Chorus}
\endsong

\newsong{Kryptonite}
\beginverse
{\nolyrics | \[Bm] | \[G6] \[Asus2] |}  
I took a walk around the world to ease my troubled mind,
I left my body lyin somewhere in the sands of time.
I watched the world float to the dark side of the moon,
I feel there's nothin I can do,     yeah.
\endverse
\beginverse
I watched the world foat to the dark side of the moon. 
After all I knew it had to be somethin to do with you. 
I really don't mind what happens now and then, 
as long as you'll be my friend at the end.
\endverse
\beginchorus
\[Bm] If I go crazy then will \[G6]you still call me \[Asus2]superman.
If I'm alive and well will you be there a holdin my hand,
I'll keep you by my side with my super human might, Kryptonite.
\endchorus
\beginverse 
You call me strong, you call me weak, but still your secrets I will keep,
you took for granted all the times I never let you down. 
You stumble again and bump your head, if not for me then you'd be dead.
I picked you up and put you back on solid ground.
\endverse
\textnote{Chorus}
\beginverse*
I took a walk around the world to ease my troubled mind,
I left my body lyin somewhere in the sands of time.
I watched the world float to the dark side of the moon,
I feel there's nothin I can do,     yeah.
\endverse
\textnote{Chorus}
\endsong