% Jonathan Coulton (Portal)

\newsong{Still Alive}
\beginverse*
{\nolyrics \[D] \[Bm] \[D] \[Bm]}
\endverse

\beginverse
This was a \[D]triumph. \[Bm] \[D]
I'm \[Bm]making a note \[D] here:
\[Bm]HUGE SUCCESS. \[Dm] \[Bm]
It's \[Em]hard to over-\[A7]state my satis-\[D]faction. \[Bm]
\endverse
\beginverse*
Aperture Science. \[D] \[Bm]
\[D] We \[Bm]do what we must \[D] because \[Bm] we can. \[D] \[Bm]
\[Em]For the good of \[A7]all of us
Except the \[B&]ones who are dead.
\endverse
\beginchorus
But there's \[F]no sense \[C]crying over \[B&]every mis-\[F]take.
You just \[F]keep on \[C]trying till you \[B&]run out of \[F]cake.
And the \[Gm]science gets \[C]done and you \[F]make a neat \[Dm]gun.
For the \[B&]people who are \[A7] still alive.
\endchorus
\beginverse
I'm not even angry.
I'm being so sincere right now.
Even though you broke my heart and killed me.
\endverse
\beginverse*
And tore me to pieces.
And threw every piece into a fire.
As they burned it hurt because
I was so happy for you!
\endverse
\beginchorus
Now these points of data make a beautiful line.
And we're out of beta, we're releasing on time.
So I'm GLaD I got burned.
Think of all the things we learned
For the people who are still alive.
\endchorus
\beginverse
Go ahead and leave me.
I think I prefer to stay inside.
Maybe you'll find someone else to help you.
\endverse
\beginverse*
Maybe Black Mesa...
THAT WAS A JOKE. Haha. FAT CHANCE.
Anyway, this cake is great.
It's so delicious and moist.
\endverse
\beginchorus
Look at me still talking when there's science to do.
When I look out there it makes me GLaD I'm not you.
I've experiments to run there is research to be done
On the people who are still alive
\endchorus
\beginverse*
And believe me I am still alive.
I'm doing science and I'm still alive.
I feel FANTASTIC and I'm still alive.
While you're dying I'll be still alive.
And when you're dead I will be still alive.
Still alive
Still alive
\endverse
\endsong

\newsong{Want You Gone}
\beginverse
Well here we are again
  It's always such a pleasure
 Remember when you tried to kill me twice?
 Oh how we laughed and laughed
 Except I wasn't laughing
 Under the circumstances I've been \[C#]shockingly nice
\endverse
\beginchorus
\[F#] \[G#m]You want your \[A#m]freedom? - \[B]Take it
\[F#] \[G#m]That's what I'm \[A#m]counting on \[B]
\[F#] \[G#m]I used to \[A#m]want you \[B]dead but
\[Bm]Now I only \[E]want you \[A]gone
\endchorus
\beginverse
  She was a lot like you
 Maybe not quite as heavy
 Now little Caroline is in here too
 One day they woke me up
 So I could live forever
 It's such a shame the same will never happen to you
\endverse
\beginchorus
You've got your short sad life left
That's what I'm counting on
I'll let you get right to it
Now I only want you gone
\endchorus
\beginverse
 Goodbye my only friend
 Oh, did you think I meant you?
 That would be funny if it weren't so sad
 Well you have been replaced
 I don't need anyone now
 When I delete you maybe I'll stop feeling so bad
\endverse
\beginchorus
Go make some new disaster
That's what I'm counting on
You're someone else's problem
\[Bm]Now I only \[E]want you gone \[A] \[F#m]
Now I only want you gone
Now I only want you gone
\endchorus
\endsong
