% Tim Minchin

\newsong{The Good Book}
\beginverse*
\[B&]Life is like an ocean voyage and our \[F]bodies are the ships
And with-\[C]out a moral compass we would \[A]all be cast a-\[Dm]drift \[Dm/C]
So to \[B&]keep us on our bearings, the \[F]Lord gave us a gift
And \[C7]like most gifts you get, it was a \[C]book
\endverse
\beginverse
I \[F]only read one book, but it's a \[B&]good book, don't you know
I \[C7]act the way I act because the Good Book tells me \[F]so
If I \[F]wanna known how \[F/E&]to be good, it's \[B&/D]to the Good Book \[B&m/D&]that I go
'Cos the \[C7]Good Book is a book and it is good and it's a \[F]book
\endverse
\beginverse
I know the Good Book's good because the Good Book says it's good
I know the Good Book knows it's good because a really good book would
You wouldn't cook without a cookbook and I think it's understood
You can't be good without a Good Book 'cos it's good and it's a book
And it is good for cookin'
\endverse
\beginverse*
I \[Dm]tried to read some other books, but I \[A]soon gave up on that
The \[B&]paragraphs ain't numbered and they \[F]complicate the \[C]facts
I \[A]can't read Harry Potter 'cos they're \[Dm]worshipping false gods and that
And \[G]Dumbledore's a poofter and that's \[C]bad, 'cos it's not good
\endverse
\beginverse
Morality is written there in simple white and black
I feel sorry for you heathens, got to think about all that
Good is good and evil's bad and goats are good and pigs are crap
You'll find which one is which in the Good Book, 'cos it's good
And it's a book, and it's a book
\endverse
\beginverse*
I had a cat, she gave birth to a litter
The kittens were adorable and they made my family laugh
But as they grew they started misbehavin'
So I drowned the little fuckers in the bath
When the creatures in your care start being menaces
The answers can be found right there in Genesis!
Chapter \[D]6, Verse 5-7! Yee-haw!
\endverse
\beginverse*
\[G]Swing your partner by the hand, \[C]have a baby if you can
But \[D]if the voices in your head say to sacrifice your kid
To \[G]satiate your loving God's \[C]fetish for dead baby blood
It's \[D]simple faith, the Book demands, so raise that knife up in your hand!
\endverse
\beginverse
Before the Good Book made us good, there was no good way to know
If a thing was good or not that good or kind of touch and go
So God decided he'd give writing allegoric prose a go
And so he wrote a book and it was generally well-received
\endverse
\beginverse*
The \[B&]Telegraph said, ``This God is remi-\[F]niscent of the \[C]Norse.''
The \[B&]Times said, ``Kind of turgid, but I \[F]liked the bit with \[C]horses.''
The \[A]Mail said, ``Lots of massacres, a \[Dm]violent tour de force.
If you \[G]only read one book this year, then \[C]this one is a book
And it is \[D]good, and it's a book!"
\endverse
\beginverse*
Swing your daughter by the hand, but if she gets raped by a man
And refuses then to marry him, stone her to death!
\endverse
\beginverse*
If \[Em]you just close your eyes and block your \[B]ears
To the ac-\[C]cumulated knowledge of the \[G]last two thousand \[D]years
Then \[B]morally, guess what? You're off the \[Em]hook
And thank \[A]Christ you only have to read one \[D]book
\endverse
\beginverse*
\[Dm]Just because the book's contents were \[A]written generations hence
By \[Dm]hairy desert-dwelling gents \[A]squatting in their dusty tents
\[Em]Just because what Heaven said was \[B]said before they'd leavened bread
\[Em]Just 'cos Jesus couldn't read \[B]doesn't mean that we should need
When ma-\[C]nipulating human genes to al-\[G]leviate pain and fight disease
When de-\[C]ciding whether it's wrong or right to \[G]help the dyin' let go of life
Or \[D]stop a pregnancy when it's just a tiny blastocyst
There's \[B]no reason why we should take a \[Em]look
At \[D]any other \[C]book but the \[G/B]Good Book
'Cause it's \[A]good and it's a book
And it's a \[D]book and it's quite good!
\endverse
\beginverse*
\[G]Good is good and \[G/F]evil's bad
And \[C/E]kids get killed when \[Cm/E]God gets mad
You'd \[D]better take a good look at the \[G]Good Book \[D] \[G]
\endverse
\endsong

\newsong{Inflatable You}
\beginverse
Your love for me is not de-\[E&6]batable
\[ C7] Your sexual appetite's in-\[Fm7]satiable
\[B&7] You never ever make me \[Fm7]waitable
De-\[B&7]lectable, inflatable \[E&6]you. \[B&7]
\endverse
\beginverse
You don't have problems with your weight at all
You never steal food off my plate at all
I never have to masturbate at all
Unstoppable, inflatable you.
\endverse
\beginverse
You never seem to menstruate at all
So you're not angry when I'm late at all
I feel permanently felatable
Unpoppable, inflatable \[E&6]you.
\endverse
\beginchorus
With \[Ej7]you in my arms I \[C#m7]feel we could just fly a-\[G#m7]way
With the \[A]right kind of gas I \[F#m7]might even try it some 
\[G#m7]day \[C#7] \[F#m7] \[B7]
In this \[Ej7]ocean of life I'm \[C#m7]never afraid we might\[G#m7]drown
We could \[A]just float forever what-\[F#m7]ever the weather
When-\[G#m7]ever my in-\[C#7]flatable \[F#m7]lover's a-\[B7]round. \[B&7]
\endchorus
\beginverse
Your thighs and buttocks are so holdable
You always do what you are toldable
And if we argue you just foldable
Controllable consolable you.
\endverse
\beginverse
My mates all reckon you are suitable
I took you 'round to watch the foodtable
And Steve and Gary said you're rootable
Commutable, refutable you.
\endverse
\beginverse
You're never sensitive or tickley
When I rub you my skin goes prickerly
It's know an static electricity
Felicity when I'm kissing you.
\endverse
\beginchorus
Your skin is so smooth, I couldn't afford you with hair
You have all the holes real girls have got plus one for the air
Your problems are simple, I don't need my Masters in Psych
To know if you get down I just perk you right up
With a couple of squirts from the pump off my bike.
\endchorus
\beginverse
You never wake up when I snore at all
A trait which I find quite adorable
You have a box and you are storable
Ignorable, back-doorable you.
\endverse
\beginverse
Any sexual position's feasible
Although you don't bend at the knees at all
Your hooters are so firm and squeezable
Increasable, un-creasable you.
\endverse
\beginverse
You don't complain about my hairy back
Or 'bout the inches that downstairs I lack
You're not disgusted by my furry crack
Burt Bacharach, Jack Kerouac ooo.
\endverse
\beginverse
Now birth control is not an issue
I clean it all up with a tissue
I bet my jealous friend all wish you
Were insatiably inflatably theirs.
\endverse
\beginverse*
Don’t let me down.
Don’t let me down.
Don’t let me down.
And I won’t let you down.
\endverse
\endsong

\newsong{You Grew on me}
\beginverse*
{\nolyrics \[B] \[D#m] \[Em]} x2
\endverse
\beginverse
\[B] You grew on me \[D#m] like a \[E]tumour
And you \[B]spread through me like ma-\[D#m]lignant mela-\[E]noma
And now you're in my \[B]heart
\[E] Should've cut you out back at the start
\[B]
\tab{minchin_tim_yougrewonme1}
\[G#m]Now I'm a-\[F#]fraid there's no \[E]cure for me
No \[G#m]dose of e-\[F#]motional \[E]chemotherapy
Can \[D#7]halt my pathetic de-\[G#m]cline
Should've \[D#7]had you removed back when \[G#m]you were be-\[A#]nign
\[D#] \[D#/C#] \[D#/B] \[D#/A#]
\endverse
\beginverse
I picked you up like a virus
Like meningococcal meningitis
Now I can't feel my legs
When you're around I can't get out of bed
I've left it too late to risk an operation
I know there's no hope for a clean amputation
The successful removal of you
Would probably kill me too
\endverse
\beginverse
You grew on me like carcinoma \[Em]
Crept up on me like untreated glaucoma
Now I \[Em]find it hard to see
This untreated dose of you has blinded me
I should've consulted my local physician
I'm stuck now forever with this tunnel vision
My periphery is screwed
Wherever I look now, all I see is you
\[D#] \[F]
\endverse
\textnote{one whole step up}
\beginverse
\[B&]When we first \[A&]met you seemed \[G&]fickle and shallow
But my armour was no match for your poison arrow
You are wedged inside my breast
If I tried to pull you out now I think I'd bleed to death
I'm feeling short of breath
You grew on me like a tumour
And you spread through me like malignant melanoma
I guess I never knew
How fast a little \[F#m]mole can grow on  \[C#]you
\endverse
\endsong
