% Pain of Salvation

\songtodo{Ashes}
\songtodo{Chain Sling}
\songtodo{Dea Pecuniae}
\songtodo{Flame to the Moth}
\songtodo{Imago}
\songtodo{Iter Impius}
\songtodo{Linoleum}

\newsong{Meaningless}
\tab{painofsalvation_meaningless1}
\beginverse
	\[B/D#] I still \[Em]smell of \[Cm]sweat
	\[B/D#] Still the \[Em]scent of my \[Cm]giving in
	\[B/D#] Try to \[Em]feel re-\[Cm]gret
	\[B/D#] But I \[Em]want it to \[Cm]stay on my skin

	\[B/D#] I still \[Em]fanta-\[Cm]size
	\[B/D#] Close my \[Em]eyes to be \[Cm]wrong again
	\[B/D#] Still those \[Em]fuck-me \[Cm]eyes
	\[B/D#] As I'm \[Em]licking the \[D&]palm of my hand
\endverse
\beginchorus
\[Em]How the hell am I supposed to 
\[C]keep myself when you are so damn 
\[Em]far away, and everything feels 
\[C]meaningless, and I am not mine\rep{2}
\endchorus
\beginverse
I still smell of sex
Still her taste on my fingertips
Try to feel remorse
But it's hard with her wet on my lips
\endverse
\beginchorus
How the hell am I supposed to 
keep myself, when you are so damn 
far away, and everything feels 
meaningless, and I am not mine

How the hell am I supposed to 
keep myself, when you are so damn 
far away, and all I do seems
meaningless, and I am not mine
\endchorus
\beginverse*
I need something of my own
Something with a locked door
A room just for me alone
Something that I can control

\[Em] I need something of my own
\[C] I need something cutting to the
\[Am]bone, I need something that is 
\[Am]mine - \[Bm] If \[C]that must be \[D]guilt, then 
\[Em]fine! I wanted something nice, but 
\[C]fine, this guilt is a hole but it's 
\[Am]mine, I wanted something 
\[Am]nice, \[Bm] this \[C]guilt is a \[D]hole but it's 
mine!
\endverse
\endsong

\songtodo{No Way}
\songtodo{Tell Me You Don't Know}
\songtodo{To the Shoreline}

\newsong{Undertow}
\textnote{Drop D}
\beginverse
Let me go, let me go
Let me seek the answer that I need to know
Let me find a way, let me walk away
Through the Undertow
Please let me go
\endverse
\beginverse
Let me fly, let me fly
Let me rise against that blood-red velvet sky
Let me chase it all, break my wings and fall
Probably survive
So let me fly
Let me fly
\endverse
\beginverse
Let me run, let me run
Let me ride the crest of chance into the sun
You were always there, but you may lose me here
Now love me if you dare
And let me run
\endverse
\beginverse*
{\nolyrics Interlude: \[G] \[Dm] \[C] \[B&sus2]}
\[Vm]I'm a-\[VI9]live and \[Vm]I am \[IV]true to my 
\[II9]heart now, I am 
\[VIm]I, but \[VII9]why must \[VIm]truth always 
\[IV9]make me die?
\endverse
\beginverse
Let me \[D]break! Let me bleed!
Let me \[G (V)]tear myself apart I need to \[B&]breathe!
Let me lose my \[G]way! Let me walk a-\[E&]stray!
Maybe to pro-\[Dm]ceed...
Just let me \[E&]bleed!
\endverse
\beginverse
Let me drain! Let me die!
Let me break the things I love I need to cry!
Let me burn it all! Let me take my fall!
Through the cleansing fire!
Now let me die!
Let me die
\endverse
\beginverse*
Let me out
Let me fade into that pitch-black velvet night
\endverse
\endsong