% Pig With the Face of a Boy

\newsong{A Complete History of the Soviet Union, Arranged to the Melody of Tetris}
\beginverse*
To \[Dm]Moscow I came seeking \[A]fortune
 But they’re \[E$^\circ$]making me work til I’m \[Dm]dead
The \[Dm]bourgeoisie have it so \[A]easy
The \[E$^\circ$]Tsar’s putting gold on his \[A7]bread
\endverse
\beginverse*
The \[Gm]people of Moscow are \[F]hungry
But \[Em7&5]think what a feast there could \[A7]be
If \[Gm]we could create a \[F]socialist state
That \[Em7&5]cared for the people like \[A7]me:
\endverse
\beginverse
\[A7]I am the man who \[Dm]arranges the blocks
That \[A7]descend upon me from \[Dm]up above.
\[Gm] They come down and I \[F]spin them around
Til they \[A7]fit in the ground like \[Dm]hand in glove.
\endverse
\beginverse*
Sometimes it seems that to move blocks is fine
And the lines will be formed as they fall -
Then I see that I have misjudged it!
I should not have nudged it after all.
\endverse
\beginchorus
\[Dm]Can I \[A7]have a \[Dm]long one \[A7]please?
\[Dm]Why must \[A7]these in\[Dm]fernal blocks \[A7]tease?
\endchorus
\beginverse
I am the man who arranges the blocks
That continue to fall from up above.
Come Muscovite! Let the workers unite!
A collective regime of peace and love.
\endverse
\beginverse*
I work so hard in arranging the blocks
But the landlord and taxman bleed me dry
But the workers will rise! We will not compromise
For we know that the old regime must die.
\endverse
\beginchorus
Long live Lenin, kill the tsar!
We salute the sickle and star!
\endchorus
\beginverse
I am the man who arranges the blocks
That continue to fall from up above.
The food on your plate now belongs to the state
A collective regime of peace and love.
\endverse
\beginverse*
I have no choice in arranging the blocks
Under Bolshevik rule, what they say goes.
The rule of the game is we all are the same
And my blocks must create unbroken rows.
\endverse
\beginchorus
Long live Stalin! He loves you!
Sing these words, or you know what he’ll do...
\endchorus
\beginverse
I am the man who arranges the blocks
That are made by the men in Kazakhstan.
They come two weeks late and they don’t tessellate
But we’re working to Stalin’s five year plan.
\endverse
\beginverse*
I am the man who arranges the tanks
That will make all the Nazis keep away
The Fuhrer is dead, and Europe is Red!
Let us point all our guns at the USA.
\endverse
\beginchorus
We shall live forever more!
We can start a nuclear war!
\endchorus
\beginverse
I am the man who arranges the blocks
That are building a highly secret base.
Hip hip hurrah for the USSR!
We are sending our men to outer space.
\endverse
\beginverse*
I work so hard in arranging the blocks
But each night I go home to my wife in tears -
What’s the point of it all, when you’re building a wall
And in front of your eyes it disappears?
\endverse
\beginchorus
Pointless work for pointless pay
This is one game I shall not play.
\[A7]I am the man who ar\[Dm]ranges the blocks!
\endchorus
\beginverse
But tomorrow I think I’ll stay in bed.
The winter is cold, I’ve got plenty of gold
And I’m standing in line for a loaf of bread
\endverse
\beginchorus
Maybe we’d be better off
If we brought down Gorbachev
\endchorus
\beginverse
I am the man who arranges the blocks
That continue to fall from up above.
The markets are free! So much money for me!
Tell me, why should I care for peace and love?
The markets are free! So much money for me!
Tell me, why should I care for peace and love?
Peace and love, peace and love!
\endverse
\beginverse*
And now the \[D]wall is down, the \[F#m]Marxists frown
There’s \[G]foreign shops all over \[A]town
When \[D]in Red Square, well \[F#m]don’t despair
There’s \[G]Levi’s and \[A]McDonald’s there
The \[Bm]US gave us \[A]crystal meth
And \[G]Yeltsin drank him\[F#m]self to death
But \[D]now that \[F#]Putin’s \[Bm]put the \[G]boot in,
\[Em]Who’ll get \[A]in our \[D]way?
\endverse
\beginverse*
So \[D]we reject free \[F#m]enterprise
And \[G]once again the \[A]left will rise.
Pre\[D]pare the flags to \[F#m]be unfurled
For \[G]we’re seceding \[A]from the world:
We \[Bm]shall regain the \[A]Georgian soil
We \[G]shall obtain the \[F#m]Arctic oil
We \[D]shall ar\[F#]range the \[Bm]blocks and \[G]toil
For\[Em]ever \[A]and a \[D]day.
\endverse
\endsong
